Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-05-01 paper.tex
Remove DTW section

In the following section, we detail the dataset of MIDI files we scraped from the Internet and describe how we prepared a subset for training our hasher.
Our cross-modality hashing model is then described in Section \ref{sec:hashing}.
In Section \ref{sec:dtw}, we cover our fast hash sequence DTW method and its accompanying pruning techniques.
Finally, we evaluate our system's performance on the task of matching files from our MIDI dataset to entries in the Million Song Dataset \cite{bertin2011million}.

@@

\section{Fast DTW Matching of Hash Sequences}
\label{sec:dtw}

>>>>

In the following section, we detail the dataset of MIDI files we scraped from the Internet and describe how we prepared a subset for training our hasher.
Our cross-modality hashing model is then described in Section \ref{sec:hashing}.
Finally, in section \ref{sec:msd} we evaluate our system's performance on the task of matching files from our MIDI dataset to entries in the Million Song Dataset \cite{bertin2011million}.

@@
